COG-ED Manuscript

### 2022-01-19 06_Paper/COG-ED/Manuscript.Rmd

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(rmarkdown)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(rmarkdown)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package
